### 2015-04-14 targetDP/doc/data_parallel_execution.tex
more complete draft
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2632 40876441-3496-0410-a613-a2fca35b2ae2

\subsection{Implementation}
\subsubsection{C}
Holds no value.
\subsubsection{CUDA}

@@

\subsection{Implementation}
\subsubsection{C}
Holds no value.
\subsubsection{CUDA}

@@

The \verb+targetSynchronize+ function is used to block until the preceeding \verb+__targetLaunch__+ has completed.

@@

\newpage
\section{targetTLP}

@@

The \verb+__targetTLP__+ syntax is used, within a \verb+__targetEntry__+
function, to specify that the proceeding block of code should be
executed in parallel and mapped to thread level parallelism
(TLP). Note that he behaviour of this operation depends on the defined
virtual vector length (VVL), which controls the lower-level
Instruction Level Parallelsim (ILP) (see following section).

@@

\newpage
\section{targetILP}

@@

The \verb+__targetILP__+ syntax is used, within a \verb+__targetTLP__+
region, to specify that the proceeding block of code should be
executed in parallel and mapped to instruction level parallelism
(ILP), where the extent of te ILP is defined by the virtual vector length (VVL) in the targetDP implementation. 
\begin{comment}
need to document VVL in more detail somewhere and link.
\end{comment}

@@

The \verb+targetCoords3D+ function provides the 3D lattice coodinates corresponding to a specified linear index.

@@

\begin{itemize}
\item \verb+coords3D+ (output): an array of 3 integers to be populated with ther 3D coordinates.
\item \verb+extent3D+ (input): An array of 3 integers corresponding to the 3D dimensions of the lattice.
\item \verb+index+ (input): the linear index.

@@

The \verb+targetIndex3D+ function returns the linear index corresponding to a specified set of 3D lattice coodinates.

>>>>

\subsection{Implementation}
\subsubsection{C}
Holds no value.
\subsubsection{CUDA}
\verb+__global__+

@@

\subsection{Implementation}
\subsubsection{C}
Holds no value.
\subsubsection{CUDA}
\verb+__device__+

@@

The \verb+targetSynchronize+ function is used to block until the preceding \verb+__targetLaunch__+ has completed.

@@

\newpage
\section{targetTLP}\label{sec:TLP}

@@

The \verb+__targetTLP__+ syntax is used, within a \verb+__targetEntry__+
function, to specify that the proceeding block of code should be
executed in parallel and mapped to thread level parallelism
(TLP). Note that he behaviour of this operation depends on the defined
virtual vector length (VVL), which controls the lower-level
Instruction Level Parallelism (ILP) (see following section).

@@

\newpage
\section{targetILP}\label{sec:ILP}

@@

The \verb+__targetILP__+ syntax is used, within a \verb+__targetTLP__+
region, to specify that the proceeding block of code should be
executed in parallel and mapped to instruction level parallelism
(ILP), where the extent of the ILP is defined by the virtual vector length (VVL) in the targetDP implementation. 
\begin{comment}
need to document VVL in more detail somewhere and link.
\end{comment}

@@

The \verb+targetCoords3D+ function provides the 3D lattice coordinates corresponding to a specified linear index.

@@

\begin{itemize}
\item \verb+coords3D+ (output): an array of 3 integers to be populated with the 3D coordinates.
\item \verb+extent3D+ (input): An array of 3 integers corresponding to the 3D dimensions of the lattice.
\item \verb+index+ (input): the linear index.

@@

The \verb+targetIndex3D+ function returns the linear index corresponding to a specified set of 3D lattice coordinates.
